### 2017-07-01 paper.tex
tidying up

The best way to choose tools for managing lessons is
to ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion forums can improve the signal-to-noise ratio
by reducing long reply-all email exchanges.
Several open frameworks are available to facilitate development of new lessons,
such as R-based learnr (\url{https://rstudio.github.io/learnr})
or GitHub-based Morea (\url{https://morea-framework.github.io})
and DataCamp's templates (\url{https://www.datacamp.com/teach/documentation}).

>>>>

The best way to choose tools for managing lessons is
to ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion forums can improve the signal-to-noise ratio
by reducing long reply-all email exchanges.
Several open frameworks are available to facilitate development of new lessons,
such as learnr (\url{https://rstudio.github.io/learnr}),
Morea (\url{https://morea-framework.github.io}),
and DataCamp's templates (\url{https://www.datacamp.com/teach/documentation}).
